Numerical Stability of Detonations in White Dwarf Simulations

### 2019-02-06 papers/ignition/paper.tex
Add comment about effective SPH spatial resolution

Early studies on WD collisions \citep{rosswog:2009,raskin:2010,loren-aguilar:2010,
hawley:2012,garcia-senz:2013} typically had effective spatial resolutions in the
range 100--500 km, and observed detonations that convert a large amount of
carbon/oxygen material into iron-group elements. These studies varied in methodology
(Lagrangian versus Eulerian evolution, nuclear network used) and did not closely agree
on the final result of the event (see Table 4 of \cite{garcia-senz:2013} for a summary).
\cite{kushnir:2013} argued that many of these simulations featured numerically unstable
evolution, ultimately caused by the zone size being significantly larger than the length
scale over which detonations form. The detonation length scale can vary widely based
on physical conditions \citep{seitenzahl:2009,garg:2017} but is generally much
smaller than 100 km.

>>>>

Early studies on WD collisions \citep{rosswog:2009,raskin:2010,loren-aguilar:2010,
hawley:2012,garcia-senz:2013} typically had effective spatial resolutions in the
range 100--500 km \added{for the grid codes, and 10--100 km for the SPH codes}, and observed detonations that convert a large amount of
carbon/oxygen material into iron-group elements. These studies varied in methodology
(Lagrangian versus Eulerian evolution, nuclear network used) and did not closely agree
on the final result of the event (see Table 4 of \cite{garcia-senz:2013} for a summary).
\cite{kushnir:2013} argued that many of these simulations featured numerically unstable
evolution, ultimately caused by the zone size being significantly larger than the length
scale over which detonations form. The detonation length scale can vary widely based
on physical conditions \citep{seitenzahl:2009,garg:2017} but is generally \replaced{much
smaller than 100 km}{not larger than 10 km}.
